\bf Title here

### 2020-08-19 paper/paper.Rmd
change the notation for # of iteration to be j

\begin{equation}
x^{(k + 1)} = x^{(k)} + \alpha_k* d^{(k)}
\label{eq:line-search}
\end{equation}

where $d^{(k)}$ is the searching direction in iteration $k$, and $\alpha_k$ is the step-size. Strictly speaking, $\alpha_k$ is chosen by another minimisation of $f(x^{(k)} + \alpha* d^{(k)})$ with respect to $\alpha$ and theoretical results have demonstrated the global convergence of the algorithm when the exact minimisation of $\alpha_k$ is attained [@curry1944method]. In practice, this second minimisation is rarely implemented due to its computational demanding or even the existence of such a minimisation. A more realistic approach is to impose a mandatory decrease in the objective function for each iteration: $f^{(k+1)}> f^{(k)}$ and despite we lose the guarantee on global convergence, this approach turns out to be efficient in practical problems.

@@

Modern development of the line search methods focuses on proposing different computation on the seraching direction: $d^{(k)}$ and various approximations on the step size: $\alpha_k$ catered for practical optimisation problems. The specific problem context we are interested in is called projection pursuit guided tour. 
Projection pursuit and guided tour are two separate methods in exporatory data analysis focusing on different aspects: coined by @friedman1974projection, projection pursuit detects interesting structures (i.e. clustering, outliers and skewness) in multivariate data via low dimensions projection; whilst guided tour is a particular variation in a broader class of data visualisation method called tour.

@@

Simulated annealing [@bertsimas1993simulated, @kirkpatrick1983optimization] modifies `search_better` based on a non-increasing cooling scheme $T(l)$. Given an initial $T_0$, the temperature at iteration $l$ is defined as $T(l) = \frac{T_0}{\log(l + 1)}$. When a candidate basis fails to have an index value larger than the current basis, simulated annealing gives it a second chance to be accepted with probabiliby $$P= \min\left\{\exp\left[-\frac{I_{cur} - I_{l}}{T(l)}\right],1\right\}$$ where $I_{\cdot}$ denotes the index value of a given basis. This implementation allows the algorithm to jump out of a local maximum and enables a more holistic search of the whole parameter space. This feature is particularly useful when the dimension of the projected space is smaller than the number of informative variables in the dataset (i.e. a one dimenional projection of the dataset with two informative variables). The algorithm can be written as replacing line 5-11 of Algorithm \ref{random-search} with Algorithm \ref{simulated_annealing}.

\begin{algorithm}
\SetAlgoLined
    Compute $I_{l} = f(\mathbf{A}_{l})$ and $T(l) = \frac{T_0}{\log(l + 1)}$\;
      \eIf{$I_{l} > I_{\text{cur}}$}{
        \KwRet{$\mathbf{A}_{l}$} \;
      }{
        Compute $P= \min\left\{\exp\left[-\frac{I_{\text{cur}} -I_{l}}{T(l)}\right],1\right\}$\;
        Draw $U$ from a uniform distribution: $U \sim \text{Unif(0, 1)}$\;
        \If{$P > U$}{
           \KwRet{$\mathbf{A}_{l}$} \;
        }
      }
  \caption{simulated annealing}
  \label{simulated_annealing}
\end{algorithm}

@@

\begin{algorithm}
\SetAlgoLined
\SetKwInOut{Input}{input}
  \SetKwInOut{Output}{output}
    \Input{$\mathbf{A}_{\text{cur}}$, $f$, $l_{\max}$, $n$, $\delta$}
    \Output{$\mathbf{A}_{**}$}
  initialisation\;
  Set $l = 1$\;
  \While{$l < l_{\max}$}{
    Generate $2n$ bases in $n$ random directions: $\mathbf{A}_{l}: \mathbf{A}_{l+9}$ within a small neighbourhood $\delta$\;
    Find the direction with the largest index value: $\mathbf{A}_{*}$ where $l < * < l+ 9$\;
    Construct the geodesic $\mathcal{G}$ from $\mathbf{A}_{\text{cur}}$ to $\mathbf{A}_{*}$\;
    Find $\mathbf{A}_{**}$ on the geodesic $\mathcal{G}$ that has the largest index value \;
    Compute $I_{**} = f(\mathbf{A}_{**})$, $p_{\text{diff}} = (I_{**} - I_{\text{cur}})/I_{**}$\;
      \If{$p_{\text{diff}} > 0.001$}{
         \KwRet{$\mathbf{A}_{**}$} \;
      }
    $l = l + 1$\;
  }
  \caption{search geodesic}
  \label{search-geodesic}
\end{algorithm}

>>>>

\begin{equation}
x^{(j + 1)} = x^{(j)} + \alpha_k* d^{(j)}
\label{eq:line-search}
\end{equation}

where $d^{(j)}$ is the searching direction in iteration $j$, and $\alpha_j$ is the step-size. Strictly speaking, $\alpha_k$ is chosen by another minimisation of $f(x^{(j)} + \alpha* d^{(j)})$ with respect to $\alpha$ and theoretical results have demonstrated the global convergence of the algorithm when the exact minimisation of $\alpha_j$ is attained [@curry1944method]. In practice, this second minimisation is rarely implemented due to its computational demanding or even the existence of such a minimisation. A more realistic approach is to impose a mandatory decrease in the objective function for each iteration: $f^{(j+1)}> f^{(j)}$ and despite we lose the guarantee on global convergence, this approach turns out to be efficient in practical problems.

@@

Modern development of the line search methods focuses on proposing different computation on the seraching direction: $d^{(j)}$ and various approximations on the step size: $\alpha_j$ catered for practical optimisation problems. The specific problem context we are interested in is called projection pursuit guided tour. 
Projection pursuit and guided tour are two separate methods in exporatory data analysis focusing on different aspects: coined by @friedman1974projection, projection pursuit detects interesting structures (i.e. clustering, outliers and skewness) in multivariate data via low dimensions projection; whilst guided tour is a particular variation in a broader class of data visualisation method called tour.

@@

Simulated annealing [@bertsimas1993simulated, @kirkpatrick1983optimization] modifies `search_better` based on a non-increasing cooling scheme $T(j)$. Given an initial $T_0$, the temperature at iteration $k$ is defined as $T(j) = \frac{T_0}{\log(j + 1)}$. When a candidate basis fails to have an index value larger than the current basis, simulated annealing gives it a second chance to be accepted with probabiliby $$P= \min\left\{\exp\left[-\frac{I_{cur} - I_{j}}{T(j)}\right],1\right\}$$ where $I_{(\cdot)}$ denotes the index value of a given basis. This implementation allows the algorithm to jump out of a local maximum and enables a more holistic search of the whole parameter space. This feature is particularly useful when the dimension of the projected space is smaller than the number of informative variables in the dataset (i.e. a one dimenional projection of the dataset with two informative variables). The algorithm can be written as replacing line 5-11 of Algorithm \ref{random-search} with Algorithm \ref{simulated_annealing}.

\begin{algorithm}
\SetAlgoLined
    Compute $I_{j} = f(\mathbf{A}_{j})$ and $T(k) = \frac{T_0}{\log(j + 1)}$\;
      \eIf{$I_{j} > I_{\text{cur}}$}{
        \KwRet{$\mathbf{A}_{j}$} \;
      }{
        Compute $P= \min\left\{\exp\left[-\frac{I_{\text{cur}} -I_{j}}{T(j)}\right],1\right\}$\;
        Draw $U$ from a uniform distribution: $U \sim \text{Unif(0, 1)}$\;
        \If{$P > U$}{
           \KwRet{$\mathbf{A}_{j}$} \;
        }
      }
  \caption{simulated annealing}
  \label{simulated_annealing}
\end{algorithm}

@@

\begin{algorithm}
\SetAlgoLined
\SetKwInOut{Input}{input}
  \SetKwInOut{Output}{output}
    \Input{$\mathbf{A}_{\text{cur}}$, $f$, $j_{\max}$, $n$, $\delta$}
    \Output{$\mathbf{A}_{**}$}
  initialisation\;
  Set $j = 1$\;
  \While{$j < j_{\max}$}{
    Generate $2n$ bases in $n$ random directions: $\mathbf{A}_{j}: \mathbf{A}_{j+9}$ within a small neighbourhood $\delta$\;
    Find the direction with the largest index value: $\mathbf{A}_{*}$ where $j < * < j+ 9$\;
    Construct the geodesic $\mathcal{G}$ from $\mathbf{A}_{\text{cur}}$ to $\mathbf{A}_{*}$\;
    Find $\mathbf{A}_{**}$ on the geodesic $\mathcal{G}$ that has the largest index value \;
    Compute $I_{**} = f(\mathbf{A}_{**})$, $p_{\text{diff}} = (I_{**} - I_{\text{cur}})/I_{**}$\;
      \If{$p_{\text{diff}} > 0.001$}{
         \KwRet{$\mathbf{A}_{**}$} \;
      }
    $j = j + 1$\;
  }
  \caption{search geodesic}
  \label{search-geodesic}
\end{algorithm}

### 2020-08-19 paper/paper.tex
change the notation for # of iteration to be j

\begin{equation}
x^{(k + 1)} = x^{(k)} + \alpha_k* d^{(k)}
\label{eq:line-search}
\end{equation}

where \(d^{(k)}\) is the searching direction in iteration \(k\), and
\(\alpha_k\) is the step-size. Strictly speaking, \(\alpha_k\) is chosen
by another minimisation of \(f(x^{(k)} + \alpha* d^{(k)})\) with respect
to \(\alpha\) and theoretical results have demonstrated the global
convergence of the algorithm when the exact minimisation of \(\alpha_k\)
is attained \citep{curry1944method}. In practice, this second
minimisation is rarely implemented due to its computational demanding or
even the existence of such a minimisation. A more realistic approach is
to impose a mandatory decrease in the objective function for each
iteration: \(f^{(k+1)}> f^{(k)}\) and despite we lose the guarantee on
global convergence, this approach turns out to be efficient in practical
problems.

@@

Modern development of the line search methods focuses on proposing
different computation on the seraching direction: \(d^{(k)}\) and
various approximations on the step size: \(\alpha_k\) catered for
practical optimisation problems. The specific problem context we are
interested in is called projection pursuit guided tour. Projection
pursuit and guided tour are two separate methods in exporatory data
analysis focusing on different aspects: coined by
\citet{friedman1974projection}, projection pursuit detects interesting
structures (i.e.~clustering, outliers and skewness) in multivariate data
via low dimensions projection; whilst guided tour is a particular
variation in a broader class of data visualisation method called tour.

@@

Simulated annealing
\citep[\citet{kirkpatrick1983optimization}]{bertsimas1993simulated}
modifies \texttt{search\_better} based on a non-increasing cooling
scheme \(T(l)\). Given an initial \(T_0\), the temperature at iteration
\(l\) is defined as \(T(l) = \frac{T_0}{\log(l + 1)}\). When a candidate
basis fails to have an index value larger than the current basis,
simulated annealing gives it a second chance to be accepted with
probabiliby
\[P= \min\left\{\exp\left[-\frac{I_{cur} - I_{l}}{T(l)}\right],1\right\}\]
where \(I_{\cdot}\) denotes the index value of a given basis. This
implementation allows the algorithm to jump out of a local maximum and
enables a more holistic search of the whole parameter space. This
feature is particularly useful when the dimension of the projected space
is smaller than the number of informative variables in the dataset
(i.e.~a one dimenional projection of the dataset with two informative
variables). The algorithm can be written as replacing line 5-11 of
Algorithm \ref{random-search} with Algorithm \ref{simulated_annealing}.

\begin{algorithm}
\SetAlgoLined
    Compute $I_{l} = f(\mathbf{A}_{l})$ and $T(l) = \frac{T_0}{\log(l + 1)}$\;
      \eIf{$I_{l} > I_{\text{cur}}$}{
        \KwRet{$\mathbf{A}_{l}$} \;
      }{
        Compute $P= \min\left\{\exp\left[-\frac{I_{\text{cur}} -I_{l}}{T(l)}\right],1\right\}$\;
        Draw $U$ from a uniform distribution: $U \sim \text{Unif(0, 1)}$\;
        \If{$P > U$}{
           \KwRet{$\mathbf{A}_{l}$} \;
        }
      }
  \caption{simulated annealing}
  \label{simulated_annealing}
\end{algorithm}

>>>>

\begin{equation}
x^{(j + 1)} = x^{(j)} + \alpha_k* d^{(j)}
\label{eq:line-search}
\end{equation}

where \(d^{(j)}\) is the searching direction in iteration \(j\), and
\(\alpha_j\) is the step-size. Strictly speaking, \(\alpha_k\) is chosen
by another minimisation of \(f(x^{(j)} + \alpha* d^{(j)})\) with respect
to \(\alpha\) and theoretical results have demonstrated the global
convergence of the algorithm when the exact minimisation of \(\alpha_j\)
is attained \citep{curry1944method}. In practice, this second
minimisation is rarely implemented due to its computational demanding or
even the existence of such a minimisation. A more realistic approach is
to impose a mandatory decrease in the objective function for each
iteration: \(f^{(j+1)}> f^{(j)}\) and despite we lose the guarantee on
global convergence, this approach turns out to be efficient in practical
problems.

@@

Modern development of the line search methods focuses on proposing
different computation on the seraching direction: \(d^{(j)}\) and
various approximations on the step size: \(\alpha_j\) catered for
practical optimisation problems. The specific problem context we are
interested in is called projection pursuit guided tour. Projection
pursuit and guided tour are two separate methods in exporatory data
analysis focusing on different aspects: coined by
\citet{friedman1974projection}, projection pursuit detects interesting
structures (i.e.~clustering, outliers and skewness) in multivariate data
via low dimensions projection; whilst guided tour is a particular
variation in a broader class of data visualisation method called tour.

@@

Simulated annealing
\citep[\citet{kirkpatrick1983optimization}]{bertsimas1993simulated}
modifies \texttt{search\_better} based on a non-increasing cooling
scheme \(T(j)\). Given an initial \(T_0\), the temperature at iteration
\(k\) is defined as \(T(j) = \frac{T_0}{\log(j + 1)}\). When a candidate
basis fails to have an index value larger than the current basis,
simulated annealing gives it a second chance to be accepted with
probabiliby
\[P= \min\left\{\exp\left[-\frac{I_{cur} - I_{j}}{T(j)}\right],1\right\}\]
where \(I_{(\cdot)}\) denotes the index value of a given basis. This
implementation allows the algorithm to jump out of a local maximum and
enables a more holistic search of the whole parameter space. This
feature is particularly useful when the dimension of the projected space
is smaller than the number of informative variables in the dataset
(i.e.~a one dimenional projection of the dataset with two informative
variables). The algorithm can be written as replacing line 5-11 of
Algorithm \ref{random-search} with Algorithm \ref{simulated_annealing}.

\begin{algorithm}
\SetAlgoLined
    Compute $I_{j} = f(\mathbf{A}_{j})$ and $T(k) = \frac{T_0}{\log(j + 1)}$\;
      \eIf{$I_{j} > I_{\text{cur}}$}{
        \KwRet{$\mathbf{A}_{j}$} \;
      }{
        Compute $P= \min\left\{\exp\left[-\frac{I_{\text{cur}} -I_{j}}{T(j)}\right],1\right\}$\;
        Draw $U$ from a uniform distribution: $U \sim \text{Unif(0, 1)}$\;
        \If{$P > U$}{
           \KwRet{$\mathbf{A}_{j}$} \;
        }
      }
  \caption{simulated annealing}
  \label{simulated_annealing}
\end{algorithm}
